PoVaTiM: A Possibilistic Valid-Time Model \\ \vspace*{0.04truein}

### 2012-05-23 ijcis-pos-model/sources/abstract.tex
First minor changes suggested by Nicolas and Olga.
Only introduction and abstract.

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage[dvips]{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{color}

\hyphenation{pro-per-ties}
\hyphenation{ge-ne-ral-ly}
\hyphenation{pre-fe-ren-ces}
\hyphenation{u-sing}
\hyphenation{pu-nish-ment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsfonts}		% math fonts.

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\Pow}{\mathcal{P}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\bool}{\operatorname*{\mathcal{B}}}
\newcommand{\Pos}{\operatorname{Pos}}
\newcommand{\Nec}{\operatorname{Nec}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\Nat}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\begin{document}

\title*{Aspects of Dealing with Imperfect Data in Temporal Databases}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Jos\'e Pons \and Christophe Billiet \and Olga Pons \and Guy De Tr\'e}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%\institute{
%Jos\'e Pons \at Department of Computer Science and Artificial Intelligence, Escuela T\'ecnica Superior de Ingenier\'ia Inform\'atica, Universidad de Granada,  C/Periodista Daniel Saucedo Aranda s/n, E-18071, Granada, Spain.
%\email{jpons@decsai.ugr.es}
%\and Christophe Billiet \at Department of Telecommunications and Information Processing, Ghent University, St.-Pietersnieuwstraat 41, B-9000 Gent, Belgium. \email{Christophe.Billiet@telin.ugent.be}
%\and Olga Pons \at Department of Computer Science and Artificial Intelligence, Escuela T\'ecnica Superior de Ingenier\'ia Inform\'atica, Universidad de Granada,  C/Periodista Daniel Saucedo Aranda s/n, E-18071, Granada, Spain.
%\email{opc@decsai.ugr.es}
%\and Guy De Tr\'e \at Department of Telecommunications and Information Processing, Ghent University, St.-Pietersnieuwstraat 41, B-9000 Gent, Belgium. \email{Guy.DeTre@telin.ugent.be}
%}

\institute{
Jos\'e Pons, Olga Pons \at Department of Computer Science and Artificial Intelligence, Escuela T\'ecnica Superior de Ingenier\'ia Inform\'atica, Universidad de Granada,  C/Periodista Daniel Saucedo Aranda s/n, E-18071, Granada, Spain.
\email{jpons, opc@decsai.ugr.es}
\and
Christophe Billiet, Guy De Tr\'e \at Department of Telecommunications and Information Processing, Ghent University, St.-Pietersnieuwstraat 41, B-9000 Gent, Belgium. \email{Christophe.Billiet, Guy.DeTre@telin.ugent.be}
}

%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\vspace{-70pt}
%\abstract*{There exist some objects in the nature that have a time-variant (e.g. an employee's working life) or time-related (e.g. the transactions in a bank account) nature. Modelling these objects in a (relational) database is possible, but the time-related attributes have an impact on the consistency of the entire database. Therefore, some temporal database models have been proposed to deal with this. These models deal both with the problem of representation and querying. Time itself is a source of imprecision / vagueness / uncertainty since the measures of time are inherently imprecise. Humans beings manage the time with imprecision and vagueness. Nevertheless, the amount of uncertainty in the temporal indications are defined by socially well-known boundaries. Several proposals for dealing with imprecision in time have been done: some proposals consider the basis of the system the imprecision related to the conversion of diferent time points and intervals. While some other proposals consider the specification of the time as the source of imprecision: the time points are ill-known.}

\abstract*{
In reality, some objects or concepts have properties with a time-variant or time-related nature. Modelling these kinds of objects or concepts in a (relational) database schema is possible, but time-variant and time-related attributes have an impact on the consistency of the entire database. Therefore, temporal database models have been proposed to deal with this. Time itself can be at the source of imprecision, vagueness and uncertainty, since existing time measuring devices are inherently imperfect. Accordingly, human beings manage time using temporal indications and temporal notions, which may contain imprecision, vagueness and uncertainty. However, the imperfection in human-used temporal indications is supported by human interpretation, whereas information systems need extraordinary support for this. Several proposals for dealing with such imperfections when modelling temporal aspects exist. Some of these proposals consider the basis of the system to be the conversion of the specificity of temporal notions between used temporal expressions. Other proposals consider the temporal indications in the used temporal expressions to be the source of imperfection. In this chapter, an overview is given, concerning the basic concepts and issues related to the modelling of time as such or in (relational) database models and the imperfections that may arise during or as a result of this modelling. Next to this, a novel and currently researched technique for handling some of these imperfections is presented.
}

\abstract{
In reality, some objects or concepts have properties with a time-variant or time-related nature. Modelling these kinds of objects or concepts in a (relational) database schema is possible, but time-variant and time-related attributes have an impact on the consistency of the entire database. Therefore, temporal database models have been proposed to deal with this. Time itself can be at the source of imprecision, vagueness and uncertainty, since existing time measuring devices are inherently imperfect. Accordingly, human beings manage time using temporal indications and temporal notions, which may contain imprecision, vagueness and uncertainty. However, the imperfection in human-used temporal indications is supported by human interpretation, whereas information systems need extraordinary support for this. Several proposals for dealing with such imperfections when modelling temporal aspects exist. Some of these proposals consider the basis of the system to be the conversion of the specificity of temporal notions between used temporal expressions. Other proposals consider the temporal indications in the used temporal expressions to be the source of imperfection. In this chapter, an overview is given, concerning the basic concepts and issues related to the modelling of time as such or in (relational) database models and the imperfections that may arise during or as a result of this modelling. Next to this, a novel and currently researched technique for handling some of these imperfections is presented.
}

\section{Introduction}
\label{sec:introduction}
\input{sources/intro.tex}

\section{Basic Concepts and Issues in Time Modelling}
\label{sec:time-domain}
\input{sources/timeDomain.tex}
\def\JPicScale{1}

\section{Data Imperfections in Time Modelling}
\label{sec:fuzzy-time-mod}
\input{sources/fuzzyTimeDomain.tex}

\section{Basic Concepts and Issues in Temporal Databases}
\label{sec:temporal-databases}
\input{sources/temporalDatabases.tex}
\def\JPicScale{1}

\section{Data Imperfections in Temporal Databases}
\label{sec:imprecision-uncertainty}
\input{sources/fuzzyTemporalDatabases.tex}

%\section{Bipolarity on temporal databases}
%\label{sec:bipolarity}
%\input{sources/bipolarity.tex}
\def\JPicScale{1}
\section{Conclusions and Further Research}
\label{sec:further-research-work}
\input{sources/frw.tex}
\def\JPicScale{1}
\section*{Acknowledgements}
Part of this research is supported by the grant BES-2009-013805 within the research project TIN2008-02066: \emph{Fuzzy Temporal Information treatment in relational DBMS}.

\input{referenc}
\def\JPicScale{0.5}

%\newpage
%\section*{Appendix: Introduction to fuzzy logic}
%\label{app:fuzzy-logic}
%\input{sources/fuzzylogic.tex}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
%
% ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%
In reality, some objects or concepts have properties with a time-variant or time-related nature. Modelling these kinds of objects or concepts in a (relational) database schema is possible, but time-variant and time-related attributes have an impact on the consistency of the entire database. Therefore, temporal database models have been proposed to deal with this. Time itself can be at the source of imprecision, vagueness and uncertainty, since existing time measuring devices are inherently imperfect. Accordingly, human beings manage time using temporal indications and temporal notions, which may contain imprecision, vagueness and uncertainty. However, the imperfection in human-used temporal indications is supported by human interpretation, whereas information systems need support for this. Several proposals for dealing with such imperfections when modelling temporal aspects exist. Some of these proposals transform the temporal expression into a compact representation. Other proposals consider the temporal indications in the used temporal expressions to be the source of imperfection. 
In this work we present a novel model to deal with imperfections in valid-time databases. Next to that, the data manipulation language, \emph{DML} is defined and implemented.
